---
title: "binomial-package"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{binomial-package}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(binomial)
```


## Finding the number of combinations in which k successes can occur in n trials
```{r}
bin_choose(10, 0.5)
```


## Finding the binomial probability for particular values

```{r}
bin_probability(success = 2, trials = 5, prob = 0.5)


bin_probability(success = 0:2, trials = 5, prob = 0.5)

```


## Finding the binomial distribution
```{r}
bin_distribution(trials = 5, prob = 0.5)
```

## Graphing the binomial distribution
```{r}
plot(bin_distribution(trials = 5, prob = 0.5))
```

## Finding the cumulative density of the binomial distribution
```{r}
bin_cumulative(trials = 5, prob = 0.5)
```

## Graphing the cumulative density of the binomial distribution
```{r}
plot(bin_cumulative(trials = 5, prob = 0.5))
```


## Creating a binomial random object

```{r}
bin_variable(10, 0.5)
```

## Printing the measure of summary
```{r}
summary(bin_variable(10, 0.5))
```

## Individual measure of summary
```{r}
bin_mean(10, 0.3)
bin_variance(10, 0.3)
bin_mode(10, 0.3)
bin_skewness(10, 0.3)
bin_kurtosis(10, 0.3)
```

